---
title: "burnout_datacleaning"
author: "Rachel Brynsvold"
date: "7/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read in, view

```{r cars}
#read in data
library(readr)
burnout_orig = read_csv("train.csv")

#create copy to edit
burnout_cl = burnout_orig

#check structure of as-read
str(burnout_orig)
```

## Examine, clean each field

#### `Employee ID`
Index field, no action necessary

#### `Date of joining`
Already date formatted; below is code (not evaluated) for a `Days in Org'` field 
if needed in the future

```{r, eval = FALSE}
#ran model with `Days in Org` and with `Date of Joining` and got same results
#so not adding, but wanted to leave the code in case we do find we want it for some reason

#dataset goes from 1/1/2008 to 12/31/2008
min(burnout_orig$"Date of Joining")
max(burnout_orig$"Date of Joining")

end_date = max(burnout_orig$"Date of Joining")
#min(burnout_orig$"Date of Joining")

burnout_cl$"Days in Org" = as.numeric(end_date - 
                                        burnout_orig$"Date of Joining")
burnout_cl$"Days in Org"[1:24]

hist(burnout_cl$"Date of Joining", col = "lightblue",
     main = "Histogram of Date of Joining field", 
     breaks = 'months',
     xlab = "Date of Joining" )
```

#### `Gender`
Only 2 unique values; should be a factor

```{r}
unique(burnout_orig$"Gender")
is.factor(burnout_orig$"Gender")

burnout_cl$"Gender" = as.factor(burnout_orig$"Gender")
is.factor(burnout_cl$"Gender")
```
       
#### `Company Type`
Only 2 unique values; should be a factor

```{r}
unique(burnout_orig$"Company Type")
is.factor(burnout_orig$"Company Type")

burnout_cl$"Company Type" = as.factor(burnout_orig$"Company Type")
is.factor(burnout_cl$"Company Type")
```

#### `WFH Setup Available`
Only 2 unique values; should be a factor

```{r}
unique(burnout_orig$"WFH Setup Available")
is.factor(burnout_orig$"WFH Setup Available")

burnout_cl$"WFH Setup Available" = as.factor(burnout_orig$"WFH Setup Available")
is.factor(burnout_cl$"WFH Setup Available")

#TODO - decide
#consider changing levels so Yes = 2?
#as.numeric(burnout_cl$"WFH Setup Available")
#does not dictate the positive class though
```

The remainder of the fields are all numerical values where, per the data 
dictionary, the values (whether continuous or integer) exist on a scale (eg
higher Designation value translates to higher in the organization).  Therefore,
for these fields we will be checking distributions and examining/handling NA's.

#### `Designation`
No NA's; no cleaning action needed

```{r}
unique(burnout_orig$"Designation")
sum(is.na(burnout_orig$"Designation"))

hist(burnout_cl$"Designation", col = "lightblue", probability = TRUE,
     main = "Histogram of Designation field", 
     xlab = "Designation" )
```

#### `Resource Allocation` 
Proportion of NA's deemed acceptable for modeling

```{r}
sum(is.na(burnout_orig$"Resource Allocation"))
ra_na_proportion = sum(is.na(burnout_orig$"Resource Allocation")) / 
                            nrow(burnout_orig)

hist(burnout_cl$"Resource Allocation", col = "lightblue", probability = TRUE,
     main = "Histogram of Resource Allocation field", 
     xlab = "Resource Allocation")
```
     
`r signif(ra_na_proportion * 100, 3)`% of `Resource Allocation` values are NA.


#### `Mental Fatigue Score`
Proportion of NA's deemed acceptable for modeling

```{r}
sum(is.na(burnout_orig$"Mental Fatigue Score"))
mf_na_proportion = sum(is.na(burnout_orig$"Mental Fatigue Score")) / 
                            nrow(burnout_orig)

hist(burnout_cl$"Mental Fatigue Score", col = "lightblue", probability = TRUE,
     main = "Histogram of Mental Fatigue Score field", 
     xlab = "Mental Fatigue Score")
```
     
`r signif(mf_na_proportion * 100, 3)`% of `Mental Fatigue Score` values are NA.

#### `Burn Rate`
Records with no target value for the target field are of no use for training.  
Should drop these records.

```{r}
sum(is.na(burnout_orig$"Burn Rate"))
br_na_proportion = sum(is.na(burnout_orig$"Burn Rate")) / 
                            nrow(burnout_orig)
```
     
`r signif(br_na_proportion * 100, 3)`% of `Burn Rate` values are NA.

```{r}
#I've dropped these vals, but lm will drop any fields containing null by default
#conceptually it seems important to drop, but practically it makes no difference,
#and changing the length of the dataset could cause headaches down the line

burnout_cl = burnout_cl[!is.na(burnout_orig$"Burn Rate"), ]
#confirm drop
sum(is.na(burnout_cl$"Burn Rate"))

hist(burnout_cl$"Burn Rate", col = "lightblue", probability = TRUE,
     main = "Histogram of Burn Rate field", 
     xlab = "Burn Rate")
```

## Cleaning Wrap-up

After dropping the records with `Burn Rate` NA, we should recalculate the NA
proportions we calculated above.

```{r}
recalc_mf_na_proportion = sum(is.na(burnout_cl$"Mental Fatigue Score")) / 
                            nrow(burnout_cl)
recalc_ra_na_proportion = sum(is.na(burnout_cl$"Resource Allocation")) / 
                            nrow(burnout_cl)
```

After dropping, `r signif(recalc_ra_na_proportion * 100, 3)`% of 
`Resource Allocation` values are NA.    
After dropping, `r signif(recalc_mf_na_proportion * 100, 3)`% of 
`Mental Fatigue Score` values are NA.    

Final look at the cleaned dataset: 

```{r}
str(burnout_cl)
```


```{r}
#running a basic model to check that cleaning yielded a usable dataset
#use na.exclude to handle remaining NA's (reference: https://stats.stackexchange.com/questions/492955/should-i-use-na-omit-or-na-exclude-in-a-linear-model-in-r)

test = lm(`Burn Rate` ~ `Date of Joining` + Gender + `Company Type` + `WFH Setup Available`
                + Designation + `Resource Allocation` + `Mental Fatigue Score`, 
   data = burnout_cl, na.action = na.exclude)
summary(test)
```


## Test write out/read back in
```{r}
#Does not read back in the same as it was written out
#It appears we need to preface the modeling script with a condensed version of 
#this cleaning script (or set params on the read_csv call to make it match)

write_csv(burnout_cl, "train_cleaned.csv")
reread = read_csv("train_cleaned.csv")
all.equal(burnout_cl, reread)
```

